### 2022-04-18 paper/localpsf_old95.tex
about to remove old stuff from paper

If $\Aop$ is symmetric positive definite, we symmetrize $\mathbf{A}_H$ as follows
\begin{equation*}
\mathbf{A}_H^{\text{sym}} := \frac{1}{2}\left(\mathbf{A}_H + \mathbf{A}_H^T\right).
\end{equation*}
Then we compute the negative eigenvalues, of $\mathbf{A}_H$ that are less than (i.e., more negative than) a small magnitude negative cutoff value $c$, and also compute the corresponding eigenvectors. That is, the eigenpairs $\{(\lambda_i,u_i)\}_{i=1}^{N_\text{bad}}$ with
\begin{equation*}
	\lambda_i < c < 0.
\end{equation*}
These outlying eigenpairs may be computed using a Krylov method, or the randomized singular value decomposition.
We then flip the sign of these ``bad'' negative eigenvalues to be positive as follows:
\begin{equation*}
	\mathbf{A}_H^{\text{sym}+} = \mathbf{A}_H^{\text{sym}} + \sum_{i=1}^{N_\text{bad}} 2 |\lambda_i| u_i u_i^T.
\end{equation*}
The matrix $\mathbf{A}_H^{\text{sym}+}$ approximates the matrix absolute value of $\mathbf{A}_H^{\text{sym}}$. A H-matrix representation of $\mathbf{A}_H^{\text{sym}+}$ is formed using H-matrix addition, and used in place of $\mathbf{A}_H$ in further linear algebra operations.

The cutoff $c$ is required when $\Aop$ has a large number of zero eigenvalues, or a sequence of eigenvalues that cluster at zero, a situation that occurs commonly in practice. We seek to correct negative eigenvalues caused by errors in our approximation procedure. But even without our approximation, numerical rounding and discretization errors may cause large numbers of zero or near-zero eigenvalues to become slightly negative. Numerically, we cannot hope to correct these small magnitude negative eigenvalues because there are so many of them, and because the spectral gap between the smallest negative eigenvalue and the first non-negative eigenvalue is small.

>>>>

If $\Aop$ is symmetric positive definite, we symmetrize $\mathbf{A}_H$ as follows
\begin{equation*}
\mathbf{A}_H^{\text{sym}} := \frac{1}{2}\left(\mathbf{A}_H + \mathbf{A}_H^T\right).
\end{equation*}
Then we compute the negative eigenvalues, of $\mathbf{A}_H$ that are less than (i.e., more negative than) a small magnitude negative cutoff value $c$, and also compute the corresponding eigenvectors. That is, the eigenpairs $\{(\lambda_i,u_i)\}_{i=1}^{N_\text{bad}}$ with
\begin{equation*}
	\lambda_i < c < 0.
\end{equation*}
These outlying ``bad'' eigenpairs may be computed using a Krylov method (we use Lanczos), or the randomized singular value decomposition.
We then flip the sign of these negative eigenvalues to be positive as follows:
\begin{equation*}
	\mathbf{A}_H^{\text{sym}+} = \mathbf{A}_H^{\text{sym}} + \sum_{i=1}^{N_\text{bad}} 2 |\lambda_i| u_i u_i^T.
\end{equation*}
The matrix $\mathbf{A}_H^{\text{sym}+}$ approximates the matrix absolute value of $\mathbf{A}_H^{\text{sym}}$. A H-matrix representation of $\mathbf{A}_H^{\text{sym}+}$ is formed using H-matrix addition, and used in place of $\mathbf{A}_H$ in further linear algebra operations.

The cutoff $c$ is required when $\Aop$ has a large number of zero eigenvalues, or a sequence of eigenvalues that cluster at zero, a situation that occurs commonly in practice. We seek to correct negative eigenvalues caused by errors in our approximation procedure. But even without our approximation, rounding and discretization errors may cause large numbers of zero or near-zero eigenvalues to become slightly negative. Numerically, we cannot hope to correct these slightly negative eigenvalues because there are so many of them, and because the spectral gap between the smallest negative eigenvalue and the first non-negative eigenvalue is small.
